Manuscript

### 2018-10-23 manuscript.Rmd
updated manuscript.Rmd/html

---
title: "Manuscript"
author: "Sally Claridge"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    theme: cerulean
    number_sections: true
    toc: true
    toc_depth: 4
    toc_float:
      collapsed: true
    code_folding: hide
    pandoc_args: [
      "+RTS", "-K2048m",
      "-RTS"
    ]
---

@@

  plot <- ggplot(data = use_data, aes(x = Mutation_Status_Nonsilent, y = AUC)) +
    facet_wrap(~ Hugo_Symbol, drop = FALSE, nrow = 1) +
    geom_boxplot(mapping = aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85), outlier.shape = 3, outlier.size = 0.5) +
    scale_fill_manual(values = use_color) +
    guides(color = FALSE) +
    geom_text(data = label_text, mapping = aes(x = 1.5, y = max(use_data$AUC), label = p.signif), nudge_y = 0.2) +
    theme(legend.position = "top", axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
    labs(fill = "Mutation Status", y = "AUC", x = "Mutation Status", title = paste0(toupper(dataset), ": ", drug))
  return(plot)
}
```

@@

knitr::kable(filter(crispr_signif_g2p_gene, p < 0.1)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results for Level A point mutations, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

knitr::kable(filter(crispr_signif_g2p_lineage, p < 0.01)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing non-silent mutant vs other cell lines by lineage, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

crispr_data_signif_g2p_lineage_plot <- ggplot(data = crispr_data_signif_g2p_lineage, aes(x = group_general_lineage_name, y = Score)) +
  facet_wrap(~ Hugo_Symbol, nrow = 4, scales = "free_y") +
  geom_point(aes(color = Mutation_Status_Nonsilent), alpha = 0.5) +
  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
  scale_color_manual(values = crispr_data_signif_g2p_lineage_color) +
  geom_text(data = crispr_data_signif_g2p_lineage_text, mapping = aes(x = group_general_lineage_name, y = Text_y, label = p.signif), angle = 90, nudge_y = 0.1) +
  theme(legend.position = "top", axis.text.x = element_text(angle = 90, hjust = 1, vjust = 1, size = 10)) +
  labs(y = "CERES Score",
       x = "Lineage",
       color = "Mutation Status",
       title = "CERES score by cell line lineage for significant Level A G2P genes",
       subtitle = "Genes with adjusted p-values < 0.3 are shown.\nBH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001\nGenes are sorted by increasing lineage-agnostic p-value.")
crispr_data_signif_g2p_lineage_plot

@@

knitr::kable(ccle_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for Level A point mutations, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

knitr::kable(ccle_signif_g2p_ByDrug_all[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: by-drug Wilcoxon test results for Level A point mutations, (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

knitr::kable(ctrp_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for Level A point mutations, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

knitr::kable(ctrp_signif_g2p_ByDrug_all[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: by-drug Wilcoxon test results for Level A point mutations, (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

knitr::kable(gdsc_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for Level A point mutations, p < 0.01 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

knitr::kable(gdsc_signif_g2p_ByDrug_all[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: by-drug Wilcoxon test results for Level A point mutations, (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

```{r fig.height=4, fig.width=20}
crispr_data_g2p$Hugo_Symbol <- factor(crispr_data_g2p$Hugo_Symbol, levels = g2p_genes)
crispr_data_g2p_color <- as.character(crispr_data_g2p$Color_Nonsilent)
names(crispr_data_g2p_color) <- crispr_data_g2p$Mutation_Status_Nonsilent

@@

crispr_data_g2p_plot <- ggplot(data = crispr_data_g2p, aes(x = Mutation_Status_Nonsilent, y = Score)) +
  facet_wrap(~ Hugo_Symbol, drop = FALSE, nrow = 1) +
  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
  geom_boxplot(mapping = aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85)) +
  scale_fill_manual(values = crispr_data_g2p_color) +
  guides(color = FALSE) +
  geom_text(data = crispr_label_text, mapping = aes(x = 1.5, y = 2, label = p.signif), nudge_y = 0.1) +
  theme(legend.position = "top", axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
  labs(title = "CRISPR", fill = "Mutation Status", y = "CERES Score", x = "Mutation Status")
crispr_data_g2p_plot

# ggsave("./plots_18Q3/manuscript/crispr_data_g2p_plot.png", crispr_data_g2p_plot, device = "png", dpi = 450, width = 20, height = 4, units = "in")
```

@@

Plot code:
```{r, eval=FALSE}
ccle_drugs <- as.character(unique(ccle_data_g2p_genesfilt$Drug))
ccle_g2p_drugboxplots <- lapply(ccle_drugs, makeDrugBoxplots, dataset = "CCLE")
ccle_g2p_drugboxplots_paths <- paste0(ccle_drugs, "_ccle_drugboxplots.png")
pwalk(list(ccle_g2p_drugboxplots_paths, ccle_g2p_drugboxplots), ggsave, path = "./plots_18Q3/manuscript/ccle_g2p_drugboxplots", dpi = 450, width = 20, height = 4, units = "in")
```

Data management:
```{r, eval=TRUE}
ccle_g2p_drugboxplots <- paste0(list.files("./plots_18Q3/manuscript/ccle_g2p_drugboxplots", full.names = TRUE))
names(ccle_g2p_drugboxplots) <- str_replace_all(ccle_g2p_drugboxplots, c("_ccle_drugboxplots.png" = "", "./plots_18Q3/manuscript/ccle_g2p_drugboxplots/" = ""))
bsselect(ccle_g2p_drugboxplots, type = "img", live_search = TRUE, show_tick = TRUE, height = 300, frame_height = 275)
```

@@

Plot code:
```{r, eval=FALSE}
ctrp_drugs <- as.character(unique(ctrp_data_g2p_genesfilt$Drug))
ctrp_g2p_drugboxplots <- lapply(ctrp_drugs, makeDrugBoxplots, dataset = "ctrp")
ctrp_g2p_drugboxplots_paths <- paste0(ctrp_drugs, "_ctrp_drugboxplots.png")
pwalk(list(ctrp_g2p_drugboxplots_paths, ctrp_g2p_drugboxplots), ggsave, path = "./plots_18Q3/manuscript/ctrp_g2p_drugboxplots", dpi = 450, width = 20, height = 4, units = "in")
```

Data management:
```{r, eval=TRUE}
ctrp_g2p_drugboxplots <- paste0(list.files("./plots_18Q3/manuscript/ctrp_g2p_drugboxplots", full.names = TRUE))
names(ctrp_g2p_drugboxplots) <- str_replace_all(ctrp_g2p_drugboxplots, c("_ctrp_drugboxplots.png" = "", "./plots_18Q3/manuscript/ctrp_g2p_drugboxplots/" = ""))
bsselect(ctrp_g2p_drugboxplots, type = "img", live_search = TRUE, show_tick = TRUE, height = 300, frame_height = 275)
```

@@

Plot code:
```{r, eval=FALSE}
gdsc_drugs <- as.character(unique(gdsc_data_g2p_genesfilt$Drug))
gdsc_g2p_drugboxplots <- lapply(gdsc_drugs, makeDrugBoxplots, dataset = "gdsc")
gdsc_g2p_drugboxplots_paths <- paste0(gdsc_drugs, "_gdsc_drugboxplots.png")
pwalk(list(gdsc_g2p_drugboxplots_paths, gdsc_g2p_drugboxplots), ggsave, path = "./plots_18Q3/manuscript/gdsc_g2p_drugboxplots", dpi = 450, width = 20, height = 4, units = "in")
```

Data management:
```{r, eval=TRUE}
gdsc_g2p_drugboxplots <- paste0(list.files("./plots_18Q3/manuscript/gdsc_g2p_drugboxplots", full.names = TRUE))
names(gdsc_g2p_drugboxplots) <- str_replace_all(gdsc_g2p_drugboxplots, c("_gdsc_drugboxplots.png" = "", "./plots_18Q3/manuscript/gdsc_g2p_drugboxplots/" = ""))
bsselect(gdsc_g2p_drugboxplots, type = "img", live_search = TRUE, show_tick = TRUE, height = 300, frame_height = 275)
```

## Gene-drug associations only

>>>>

---
title: "Manuscript"
author: "Sally Claridge"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    theme: cerulean
    number_sections: true
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: true
    code_folding: hide
    pandoc_args: [
      "+RTS", "-K2048m",
      "-RTS"
    ]
---

@@

  plot <- ggplot(data = use_data, aes(x = Mutation_Status_Nonsilent, y = AUC)) +
    facet_wrap(~ Hugo_Symbol, drop = FALSE, nrow = 1) +
    geom_boxplot(mapping = aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85), outlier.shape = 3, outlier.size = 0.5) +
    scale_fill_manual(values = use_color) +
    guides(color = FALSE) +
    geom_text(data = label_text, mapping = aes(x = 1.5, y = max(use_data$AUC), label = p.signif), nudge_y = 0.2) +
    theme(strip.text.x = element_text(size = 10, angle = 45), legend.position = "top", axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
    labs(fill = "Mutation Status", y = "AUC", x = "Mutation Status", title = paste0(toupper(dataset), ": ", drug))
  return(plot)
}
```

@@

knitr::kable(crispr_signif_g2p_gene[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results for Level A point mutations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

knitr::kable(filter(crispr_signif_g2p_lineage, p < 0.1)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing non-silent mutant vs other cell lines by lineage, p < 0.1 (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

crispr_data_signif_g2p_lineage_plot <- ggplot(data = crispr_data_signif_g2p_lineage, aes(x = group_general_lineage_name, y = Score)) +
  facet_wrap(~ Hugo_Symbol, nrow = 4, scales = "free_y") +
  geom_point(aes(color = Mutation_Status_Nonsilent), alpha = 0.5) +
  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
  scale_color_manual(values = crispr_data_signif_g2p_lineage_color) +
  geom_text(data = crispr_data_signif_g2p_lineage_text, mapping = aes(x = group_general_lineage_name, y = Text_y, label = p.signif), angle = 90, nudge_y = 0.1) +
  theme(legend.position = "top", axis.text.x = element_text(angle = 90, hjust = 1, vjust = 1, size = 10)) +
  labs(y = "CERES Score",
       x = "Lineage",
       color = "Mutation Status",
       title = "CERES score by cell line lineage for significant Level A G2P genes",
       subtitle = "* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001\nGenes are sorted by increasing lineage-agnostic p-value.")
crispr_data_signif_g2p_lineage_plot

@@

knitr::kable(ccle_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: Wilcoxon test results for level A G2P drug-gene associations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

knitr::kable(ccle_signif_g2p_ByDrug_all[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: By-drug Wilcoxon test results for point mutations in level A G2P genes (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

knitr::kable(ctrp_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: Wilcoxon test results for level A G2P drug-gene associations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

knitr::kable(ctrp_signif_g2p_ByDrug_all[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: By-drug Wilcoxon test results for point mutations in level A G2P genes (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

knitr::kable(gdsc_signif_g2p[, c("Drug_Gene", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: Wilcoxon test results for level A G2P drug-gene associations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

knitr::kable(gdsc_signif_g2p_ByDrug_all[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: by-drug Wilcoxon test results for point mutations in level A G2P genes (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

```{r fig.height=5, fig.width=20}
crispr_data_g2p$Hugo_Symbol <- factor(crispr_data_g2p$Hugo_Symbol, levels = g2p_genes)
crispr_data_g2p_color <- as.character(crispr_data_g2p$Color_Nonsilent)
names(crispr_data_g2p_color) <- crispr_data_g2p$Mutation_Status_Nonsilent

@@

crispr_data_g2p_plot <- ggplot(data = crispr_data_g2p, aes(x = Mutation_Status_Nonsilent, y = Score)) +
  facet_wrap(~ Hugo_Symbol, drop = FALSE, nrow = 1) +
  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
  geom_boxplot(mapping = aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85)) +
  scale_fill_manual(values = crispr_data_g2p_color) +
  guides(color = FALSE) +
  geom_text(data = crispr_label_text, mapping = aes(x = 1.5, y = 2, label = p.signif), nudge_y = 0.1) +
  theme(strip.text.x = element_text(size = 10, angle = 45), legend.position = "top", axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
  labs(title = "CRISPR", fill = "Mutation Status", y = "CERES Score", x = "Mutation Status")
crispr_data_g2p_plot

# ggsave("./plots_18Q3/manuscript/crispr_data_g2p_plot.png", crispr_data_g2p_plot, device = "png", dpi = 450, width = 20, height = 5, units = "in")
```

@@

Plot code:
```{r, eval=FALSE}
ccle_drugs <- as.character(unique(ccle_data_g2p_genesfilt$Drug))
ccle_g2p_drugboxplots <- lapply(ccle_drugs, makeDrugBoxplots, dataset = "CCLE")
ccle_g2p_drugboxplots_paths <- paste0(ccle_drugs, "_ccle_drugboxplots.png")
pwalk(list(ccle_g2p_drugboxplots_paths, ccle_g2p_drugboxplots), ggsave, path = "./plots_18Q3/manuscript/ccle_g2p_drugboxplots", dpi = 450, width = 20, height = 5, units = "in")
```

Data management:
```{r, eval=TRUE}
ccle_g2p_drugboxplots <- paste0(list.files("./plots_18Q3/manuscript/ccle_g2p_drugboxplots", full.names = TRUE))
names(ccle_g2p_drugboxplots) <- str_replace_all(ccle_g2p_drugboxplots, c("_ccle_drugboxplots.png" = "", "./plots_18Q3/manuscript/ccle_g2p_drugboxplots/" = ""))
bsselect(ccle_g2p_drugboxplots, type = "img", live_search = TRUE, show_tick = TRUE, height = 100)
```

@@

Plot code:
```{r, eval=FALSE}
ctrp_drugs <- as.character(unique(ctrp_data_g2p_genesfilt$Drug))
ctrp_g2p_drugboxplots <- lapply(ctrp_drugs, makeDrugBoxplots, dataset = "ctrp")
ctrp_g2p_drugboxplots_paths <- paste0(ctrp_drugs, "_ctrp_drugboxplots.png")
pwalk(list(ctrp_g2p_drugboxplots_paths, ctrp_g2p_drugboxplots), ggsave, path = "./plots_18Q3/manuscript/ctrp_g2p_drugboxplots", dpi = 450, width = 20, height = 5, units = "in")
```

Data management:
```{r, eval=TRUE}
ctrp_g2p_drugboxplots <- paste0(list.files("./plots_18Q3/manuscript/ctrp_g2p_drugboxplots", full.names = TRUE))
names(ctrp_g2p_drugboxplots) <- str_replace_all(ctrp_g2p_drugboxplots, c("_ctrp_drugboxplots.png" = "", "./plots_18Q3/manuscript/ctrp_g2p_drugboxplots/" = ""))
bsselect(ctrp_g2p_drugboxplots, type = "img", live_search = TRUE, show_tick = TRUE, height = 100)
```

@@

Plot code:
```{r, eval=FALSE}
gdsc_drugs <- as.character(unique(gdsc_data_g2p_genesfilt$Drug))
gdsc_g2p_drugboxplots <- lapply(gdsc_drugs, makeDrugBoxplots, dataset = "gdsc")
gdsc_g2p_drugboxplots_paths <- paste0(gdsc_drugs, "_gdsc_drugboxplots.png")
pwalk(list(gdsc_g2p_drugboxplots_paths, gdsc_g2p_drugboxplots), ggsave, path = "./plots_18Q3/manuscript/gdsc_g2p_drugboxplots", dpi = 450, width = 20, height = 5, units = "in")
```

Data management:
```{r, eval=TRUE}
gdsc_g2p_drugboxplots <- paste0(list.files("./plots_18Q3/manuscript/gdsc_g2p_drugboxplots", full.names = TRUE))
names(gdsc_g2p_drugboxplots) <- str_replace_all(gdsc_g2p_drugboxplots, c("_gdsc_drugboxplots.png" = "", "./plots_18Q3/manuscript/gdsc_g2p_drugboxplots/" = ""))
bsselect(gdsc_g2p_drugboxplots, type = "img", live_search = TRUE, show_tick = TRUE, height = 100)
```

## G2P level A gene-drug associations only
